### 2015-08-09 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:08	14:11:37	(Sat 8.Aug)
la2pdf commit - 2015:08:08	14:13:44	(Sat 8.Aug)
la2pdf commit - 2015:08:09	15:19:42	(Sun 9.Aug)

@@

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=.2\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

>>>>

Narrow ones:
- Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.

Beamforming:
- Maximize resolution
- Minimize noise/error, both coherent and incoherent
- Minimize signal cancellation

Gauss: Miminized time-bandwidth product
  -

Rectangular
  - 
Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.

Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.

@@

\begin{figure*}[tbhp!]%\centering%
\includegraphics[width=\textwidth]{gfx/oversampling_mosaic_bounds_lca_windows_beta.pdf}%
\caption{Window parameter boundaries. Oversampled image, 19x20 windows.}\label{oversampling_mosaic_bounds}
\end{figure*}

### 2015-08-09 ThesisJo/derivations.tex
la2pdf commit - 2015:08:09	15:19:42	(Sun 9.Aug)

@@

>>>>

\begin{align}
\text{Processing Gain} &= \frac{S_o/N_o}{S_i/N_i} = \frac{A^2\big|\sumb{m}{}w_m\big|^2 \big/ \sigma_q^2\sumb{m}{}w_m^2}{A^2 / \sigma_q^2} = \frac{\big|\sumb{m}{}w_m\big|^2}{\sumb{m}{}w_m^2}
\end{align}

@@

Beamforming:
- Maximize resolution
- Minimize noise/error, both coherent and incoherent
- Minimize signal cancellation

Gauss: Miminized time-bandwidth product
  -

Rectangular
  - 
Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.

Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.
